---
title: "Week4Lecture"
author: "Zain"
date: "9/19/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Tidyverse
tidyverse package contains the ggplot library that we will use for graph. So, we will import tidyverse first

```{r}
library(tidyverse)
```
###Importing data
Let us import the dataset
```{r}
mn_homes <- read_csv("data/mn_homes.csv")
glimpse(mn_homes)
summary(mn_homes)
```
###first ggplot :)
ggplot just give you the basic background of the plot

```{r}
ggplot(data = mn_homes,mapping = aes(x=area,y=salesprice))
```
Now, let us add the actual values

```{r}
ggplot(data = mn_homes,mapping = aes(x=area,y=salesprice))+
  geom_point()+
  geom_smooth()
```
Now, let us draw three variables in our diagram

```{r}
ggplot(data = mn_homes,mapping = aes(x=area,y=salesprice,color=fireplace))+
  geom_point()
```

different variable for color
```{r}
ggplot(data = mn_homes,mapping = aes(x=area,y=salesprice,color=community))+
  geom_point()
```
Quick Revision for the last session
```{r}
ggplot(data=mn_homes, mapping = aes(x=area,y=salesprice)) +
  geom_point()
```

```{r}
ggplot(data=mn_homes, mapping = aes(x=area,y=salesprice, color=community)) +
  geom_point()
```

### Adding lables to the graph

```{r}
ggplot(data=mn_homes, mapping = aes(x=area,y=salesprice, color=community)) +
  geom_point() +
  labs(title="The relation betweem house area and the sales price (2005-2015)", x="Area of the huose in square foot", y="Sales price of houses")
```
##Faceting
Sometimes we get too much points in our graph. We can use faceting to seperate them in several graphs. for example:

```{r}
ggplot(data=mn_homes, mapping = aes(x=area,y=salesprice, color=community)) +
  geom_point() +
  facet_wrap(~community)
```


The other type of faceting is facet_grid(). It help you to categorize your charts based on two variables. For example:

```{r}
ggplot(data=mn_homes, mapping = aes(x=area,y=salesprice, color=community)) +
  geom_point() +
  facet_grid(community~beds)
```
let us get back to geom_smooth and check the linetype attribute

```{r}
ggplot(data=mn_homes, mapping = aes(x=area, y=salesprice, linetype=fireplace))+
  geom_point()+
  geom_smooth()
```
##geom_bar()
We use geom_bar with discrete variables. It ussually use on variable only

```{r}
ggplot(data=mn_homes) +
  geom_bar(mapping=aes(x=community))
```

count is the default y axis for the bar chart. However, we can change this manually to percentage. for example:

```{r}
ggplot(data=mn_homes) +
  geom_bar(mapping=aes(x=community, y=..prop.., group=1))
```

We can add more variables to bar charts using color or fill attributes

```{r}
ggplot(data=mn_homes) +
  geom_bar(mapping=aes(x=saleyear,fill=community))

```
### poistion attribute for bar chart

```{r}
ggplot(data=mn_homes) +
  geom_bar(mapping=aes(x=community,fill=fireplace),position="dodge")
```

```{r}
ggplot(data=mn_homes) +
  geom_bar(mapping=aes(x=community,fill=fireplace),position="identity", alpha=1/5)
```

